\textsf{Are large language models superhuman chemists?}

### 2024-10-24 src/tex/ms.tex
done

\begin{table}
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}

@@

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation, a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena.
We also thank Stability.AI for the access to its HPC cluster. In addition, M.S-W.'s work was supported by Intel and Merck via the AWASES programme.
K.M.J.\ is part of the NFDI consortium FAIRmat funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) – project 460197019.
K.M.J.\ thanks FutureHouse (a non-profit research organization supported by the generosity of Eric and Wendy Schmidt) for supporting \PaperQATwo run by access to the \gls{api}.
Parts of A.M.'s work was supported as part of the \enquote{SOL-AI} project funded by the Helmholtz Foundation model initative.

>>>>

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}

@@

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation, a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena.
We also thank Stability.AI for the access to its HPC cluster. In addition, M.S-W.'s work was supported by Intel and Merck via the AWASES programme.
K.M.J.\ is part of the NFDI consortium FAIRmat funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) – project 460197019.
K.M.J.\ thanks FutureHouse (a non-profit research organization supported by the generosity of Eric and Wendy Schmidt) for supporting \PaperQATwo run by access to the \gls{api}.
Parts of A.M.'s work was supported as part of the \enquote{SOL-AI} project funded by the Helmholtz Foundation model initative.
A.A.\ gratefully acknowledges financial support for this (publication/project/research) by the Fulbright U.S. Student Program, which is sponsored by the U.S. Department of State and German-American Fulbright Commission. Its contents are solely the responsibility of the author and do not necessarily represent the official views of the Fulbright Program, the Government of the United States, or the German-American Fulbright Commission.
